Exploratory analysis of context: Examples

### 2021-12-03 analysis/exploratory/context_versus_nocontext/rscripts/examples.Rmd
edited examples .rmd

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "39551:19") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

>>>>

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == "75191:67") %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```
